When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote about NIPS

In the analysis of SV difference scores, the NFC group did not reach significance as a predictor.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.

>>>>

In the analysis of SV difference scores, the NFC group did not reach significance as a predictor.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmidt et al. (2013)[-@Schmidt2013] and Blum et al. (2018)[-@Blum2018] in the same-named NIPS model.
The NIPS model describes behaviour as a function of situational affordance which is mediated by personality traits.
The behavioural variability follows an s-shaped curve that is shifted along the y-axis depending on the trait level, such that "strong" situations with low or high situational affordance elicit the least behavioural variability, while "weak" situations with moderate affordance maximize individual differences.
In our study, the situational affordance is the $n$-back level and the behaviour is the SV.
Hence, the variability in SVs increased from 1- to 4-back, and participants with higher NFC showed a more shallow decline in SVs as the situational affordance approached moderate values.
According to the NIPS model, we can expect the SVs of participants with higher and lower NFC to converge again in levels of $n>4$, since behavioural variability decreases when situational affordance is high.
The declining logistic contrast of SVs across levels resembles the asymptotic s-shaped curve of the NIPS model[@Schmidt2013;@Blum2018] and should be tested in a setting with $n$-back levels exceeding $n=4$.
